### 2017-04-13 sections/math.tex
Update on Overleaf.

Singular value decomposition (SVD) \cite{Baker2013, Kalman2002} is based on a theorem from linear algebra which says that a rectangular matrix $\mtrx{A} \in \mathbb{R}^{m \times n}$ can be decomposed into the product of three matrices - an orthogonal matrix $\mtrx{U} \in \mathbb{R}^{m \times m}$, a diagonal
matrix $\mtrx{S} \in \mathbb{R}^{m \times n}$, and the transpose of an orthogonal matrix $\mtrx{V} \in \mathbb{R}^{n \times n}$:

@@

\subsection{Randomized SVD}
In \cite{Holmes, Halko2011, Candes2009} are described randomized algorithms for constructing approximate matrix factorizations. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

Exact SVD of a $m \times n$ matrix has time complexity $O(min(mn^2, m^2n))$ using the "big-O" notation. Assume the data points are in the columns of $\mtrx{A}$ where $m \leq n$. Note that $\mtrx{AA^\mathsf{T}}$ is the dataset covariance matrix. Then a simple method is to randomly choose $k<m$ columns of $\mtrx{A}$ that form a matrix $\mtrx{B}$. Statistically, the SVD of $\mtrx{BB^\mathsf{T}}$ will be close to that of $\mtrx{AA^\mathsf{T}}$; thus it suffices to calculate the SVD of $\mtrx{B}$, the complexity of which, is only $O(k^2m)$.

% http://mathoverflow.net/questions/161252/what-is-the-time-complexity-of-truncated-svd

>>>>

Singular value decomposition (SVD) \cite{Baker2005, Kalman1996} is based on a theorem from linear algebra which says that a rectangular matrix $\mtrx{A} \in \mathbb{R}^{m \times n}$ can be decomposed into the product of three matrices - an orthogonal matrix $\mtrx{U} \in \mathbb{R}^{m \times m}$, a diagonal
matrix $\mtrx{S} \in \mathbb{R}^{m \times n}$, and the transpose of an orthogonal matrix $\mtrx{V} \in \mathbb{R}^{n \times n}$:

@@

\subsection{Randomized SVD}
In \cite{Holmes2007, Halko2011, Candes2011, Woolfe2008, Martinsson2011} are described randomized algorithms for constructing approximate matrix factorizations. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

% TODO: tenhle odstavec vyhodit
Exact SVD of a $m \times n$ matrix has time complexity $O(min(mn^2, m^2n))$ using the "big-O" notation. Assume the data points are in the columns of $\mtrx{A}$ where $m \leq n$. Note that $\mtrx{AA^\mathsf{T}}$ is the dataset covariance matrix. Then a simple method is to randomly choose $k<m$ columns of $\mtrx{A}$ that form a matrix $\mtrx{B}$. Statistically, the SVD of $\mtrx{BB^\mathsf{T}}$ will be close to that of $\mtrx{AA^\mathsf{T}}$; thus it suffices to calculate the SVD of $\mtrx{B}$, the complexity of which, is only $O(k^2m)$.
% see: http://mathoverflow.net/questions/161252/what-is-the-time-complexity-of-truncated-svd
